\tit

### 2021-02-26 paper.tex
BaanenSwierstra2020

>>>>

\item \citet{BaanenSwierstra2020} also explored correctness of regular expression matching in Agda, but from the perspective of \emph{effects} and their predicate transformer semantics.
The authors shared a common starting point with \citet{KorkutEtAl2016} and addressed differentiation on regular expressions, while separating termination from partial correctness.
Their regular expression matching function targets a free monad (later to be interpreted with suitable effect semantics) rather than propositions.
